{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-15 brains-protocol.tex
Fuse figures b and c on subtitution binning, fix figure references in tex

\begin{figure}[h]
    \centering
    \subfloat[Possible paths from occurrence to occurrence]{
	    \def\svgwidth{\linewidth}
	    \small
	    \input{images/substitution-temporal-binning-a.pdf_tex}
	    \label{fig:substitution-temporal-binning-a}
	}
	\hfill \\
    \subfloat[Binned quotation family]{
	    \def\svgwidth{\linewidth}
	    \small
	    \input{images/substitution-temporal-binning-b.pdf_tex}
	    \label{fig:substitution-temporal-binning-b}
	}
	\hfill \\
	\subfloat[XXXX]{
	    \def\svgwidth{\linewidth}
	    \small
	    \input{images/substitution-q_max.pdf_tex}
	    \label{fig:substitution-q_max}
	}
	\caption{{\bf Temporal binning of quotation families.} In bin~3, $q'$ now holds the majority and is considered the unique basis for the last occurrence of $q$ (in bin~4). This is despite the fact that $q$ also appears in bin~3 alongside $q'$, and despite it having appeared earlier at the very beginning of the quotation family (indeed in the situation shown in Figure~\ref{fig:substitution-q_max}, this seems to be the most likely scenario). Conversely, if $q$ had been the most frequent quote in bin~3, the last occurrence of $q$ in bin~4 would have been considered a faithful copy of the occurrence in bin~3.}
    \label{fig:substitution-temporal-binning}
\end{figure}

@@

Put shortly, such a model defines how many times quote occurrences can be counted as substitutions: in Figure~\ref{fig:substitution-temporal-binning-b}, occurrences of $q'$ on the 21st and 22nd are counted as substitutions, whereas the occurrence on the 23rd is not.  In practice, from the 838k initial occurrences spread into 19,621 classes of quotes, with significant redundancy (many quotes are indeed simple duplicates), we manage to mine 2,873 real substitutions obeying to this model. From these substitutions we remove those featuring stop words, minor spelling changes (e.g. center/centre, November/Nov, Senator/Sen), abbreviations, spelled out numbers; this eventually yields 476 valid substitutions.

@@

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/feature_variations-binned.png}
    \caption{\textbf{Feature variation upon substitution:} average feature of the appearing word minus $\mathcal{H}_0$ vs. average feature of the disappearing word in a substitution, with 95\% asymptotic confidence intervals.
    The overall position of the curve with respect to $y = 0$ indicates the direction of the cognitive bias.
    The fact that all the curves have slopes smaller than 1 means that the substitution operation is contractile on average: each feature will converge towards its own specific asymptotic range, which is consistent with the evolution observed in Figure~\ref{fig:timebags-evolution}.}
    \label{fig:feature-variations}
\end{figure*}

>>>>

\begin{figure}[h]
    \centering
    \subfloat[Possible paths from occurrence to occurrence]{
	    \def\svgwidth{\linewidth}
	    \small
	    \input{images/substitution-temporal-binning-a.pdf_tex}
	    \label{fig:substitution-temporal-binning-a}
	}
	\hfill \\
	\subfloat[Binned quotation family with majority rule]{
	    \def\svgwidth{\linewidth}
	    \small
	    \input{images/substitution-q_max.pdf_tex}
	    \label{fig:substitution-q_max}
	}
	\caption{{\bf Temporal binning of quotation families.} In bin~3, $q'$ now holds the majority and is considered the unique basis for the last occurrence of $q$ (in bin~4). This is despite the fact that $q$ also appears in bin~3 alongside $q'$, and despite it having appeared earlier at the very beginning of the quotation family (indeed in the situation shown in Figure~\ref{fig:substitution-q_max}, this seems to be the most likely scenario). Conversely, if $q$ had been the most frequent quote in bin~3, the last occurrence of $q$ in bin~4 would have been considered a faithful copy of the occurrence in bin~3.}
    \label{fig:substitution-temporal-binning}
\end{figure}

@@

Put shortly, such a model defines how many times quote occurrences can be counted as substitutions: in Figure~\ref{fig:substitution-q_max}, occurrences of $q'$ on the 21st and 22nd are counted as substitutions, whereas the occurrence on the 23rd is not.  In practice, from the 838k initial occurrences spread into 19,621 classes of quotes, with significant redundancy (many quotes are indeed simple duplicates), we manage to mine 2,873 real substitutions obeying to this model. From these substitutions we remove those featuring stop words, minor spelling changes (e.g. center/centre, November/Nov, Senator/Sen), abbreviations, spelled out numbers; this eventually yields 476 valid substitutions.

@@

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/feature_variations-binned.png}
    \caption{\textbf{Feature variation upon substitution:} average feature of the appearing word minus $\mathcal{H}_0$ vs. average feature of the disappearing word in a substitution, with 95\% asymptotic confidence intervals.
    The overall position of the curve with respect to $y = 0$ indicates the direction of the cognitive bias.
    The fact that all the curves have slopes smaller than 1 means that the substitution operation is contractile on average: each feature will converge towards its own specific asymptotic range.}
    \label{fig:feature-variations}
\end{figure*}
